The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex
Fixed typo in io.ascii section
tweak convolution legend to avoid greengrocer's apostrophe

The \package{astropy.io.ascii} subpackage now includes a significantly faster
Cython/C engine for reading and writing ASCII files. This is available for most
of the common formats.  On average, the new engine is about 4 to 5 times faster
than the corresponding pure-\python implementation and is often comparable to
the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
fast reader has parallel processing option that allows harnessing multiple
cores for input parsing to achieve even greater speed gains.  By default,
\texttt{read()} and \texttt{write()} will attempt to use the fast Cython/C engine
when dealing with compatible formats. Certain features of the full read
/ write interface are unavailable in the fast version, in which case the
pure-\python version will automatically be used.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  The red x's mark pixels that are set to \texttt{NaN} in the
    original data (a).  If the data are convolved with a Gaussian kernel on a
    $9\times 9$ grid using
    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
    depressed relative to their surroundings.  Finally, panel (d) shows
    \astropypkg's convolution behavior, where the missing pixels are replaced
    with values interpolated from their surroundings using the convolution
    kernel.
    \label{fig:convolution-example}
}
\end{figure}

>>>>

The \package{astropy.io.ascii} subpackage now includes a significantly faster
Cython/C engine for reading and writing ASCII files. This is available for most
of the common formats.  On average, the new engine is about 4 to 5 times faster
than the corresponding pure-\python implementation and is often comparable to
the speed of the \package{pandas} \citep{pandas} ASCII file interface.  The
fast reader has a parallel processing option that allows harnessing multiple
cores for input parsing to achieve even greater speed gains.  By default,
\texttt{read()} and \texttt{write()} will attempt to use the fast Cython/C engine
when dealing with compatible formats. Certain features of the full read
/ write interface are unavailable in the fast version, in which case the
pure-\python version will automatically be used.

@@

\begin{figure}
\includegraphics[width=\textwidth]{convolution_example}
\caption{%
    An example showing different modes of convolution available in the \python
    ecosystem.  Each red $x$ signifies a pixel that is set to \texttt{NaN} in the
    original data (a).  If the data are convolved with a Gaussian kernel on a
    $9\times 9$ grid using
    \package{scipy}'s direct convolution (b), any pixel within range of the original \texttt{NaN}
    pixels is also set to \texttt{NaN}.  Panel (c) shows what happens if the
    \texttt{NaN}s are set to zero first: the originally \texttt{NaN} regions are
    depressed relative to their surroundings.  Finally, panel (d) shows
    \astropypkg's convolution behavior, where the missing pixels are replaced
    with values interpolated from their surroundings using the convolution
    kernel.
    \label{fig:convolution-example}
}
\end{figure}
